## Quick Code Exercise

::: small
::: columns
::: {.column width="50%"}
**1. Create new data frame** (`new_trial`) and select columns `age`, `stage`, `response`, `marker`

**2. Make a basic `tbl_summary()`** summarizing by `response` variable and add the following customization:

-   For `age` make `statistic` report the`"{mean} ({min}, {max})"`

-   Use `missing` arg to remove display of missing values

**3. Now apply the following customization:**

-   add a p-value

-   bold labels and p-values ≤ .05, italicize levels

-   add an 'overall' column
:::

::: {.column width="50%" style="red"}
See documentation for help: <https://www.danieldsjoberg.com/gtsummary/>
:::
:::
:::

## Quick Code Exercise {auto-animate="true"}

::: small
::: columns
::: {.column width="50%"}
**1. Create new data frame** (`new_trial`) and select columns `age`, `stage`, `response`, `marker`

**2. Make a basic `tbl_summary()`** summarizing by `response` variable and add the following customization:

-   For `age` make `statistic` report the`"{mean} ({min}, {max})"`

-   Use `missing` arg to remove display of missing values

**3. Now apply the following customization:**

-   add a p-value

-   bold labels and p-values ≤ .05, italicize levels

-   add an 'overall' column
:::

::: {.column width="50%"}
```{r}
#| echo: true
new_trial <- select(trial, age, stage, response, marker)
```
:::
:::
:::

## Quick Code Exercise {auto-animate="true"}

::: small
::: columns
::: {.column width="50%"}
**1. Create new data frame** (`new_trial`) and select columns `age`, `stage`, `response`, `marker`

**2. Make a basic `tbl_summary()`** summarizing by `response` variable and add the following customization:

-   For `age` make `statistic` report the`"{mean} ({min}, {max})"`

-   Use `missing` arg to remove display of missing values

**3. Now apply the following customization:**

-   add a p-value

-   bold labels and p-values ≤ .05, italicize levels

-   add an 'overall' column
:::

::: {.column width="50%"}
```{r}
#| echo: true
new_trial <- select(trial, age, stage, response, marker)

new_trial %>%
  tbl_summary(by = response, 
              statistic = age ~ "{mean} ({min}, {max})", 
              missing = "no")
```
:::
:::
:::

## Quick Code Exercise {auto-animate="true"}

::: small
::: columns
::: {.column width="50%"}
**1. Create new data frame** (`new_trial`) and select columns `age`, `stage`, `response`, `marker`

**2. Make a basic `tbl_summary()`** summarizing by `response` variable and add the following customization:

-   For `age` make `statistic` report the`"{mean} ({min}, {max})"`

-   Use `missing` arg to remove display of missing values

**3. Now apply the following customization:**

-   add a p-value

-   bold labels and p-values ≤ .05, italicize levels

-   add an 'overall' column
:::

::: {.column width="50%"}
```{r}
#| echo: true
new_trial <- select(trial, age, stage, response, marker)

new_trial %>%
  tbl_summary(by = response, 
              statistic = age ~ "{mean} ({min}, {max})", 
              missing = "no") %>%
  add_p() %>%
  bold_labels() %>%
  bold_p() %>%
  italicize_levels() %>%
  add_overall() 
```
:::
:::
:::